Classless Java

### 2015-11-22 paper/sections/CaseStudy.tex
case study section summary

\section{Case Studies}
Haoyuan and Yanlin

>>>>

\section{Case Studies}
In this section we conduct three case studies which reveals various advantages
using \mixin annotation. 1st case study provides a easy and straightforward way
to solve the Expression Problem. 2nd case study models a simple game and the
comparison between our approach and others shows that code amount is reduced
tremendously using \mixin. 3rd case study models an embedded DSL for SQL
languages with fluent interfaces and shows that \mixin not only removes verbol
code for defining fluent interfaces but also does implicit refinement along
extension.
